### 2004-11-09 doc/Simulation_and_Control_using_Supremica/automationobjects.tex
*** empty log message ***

%% Intro
With the function blocks the main technological problem of
distributed automation has been solved. A general framework
for development and deployment of distributed automation
system has been developed and established. What is still
needed is a way of encapsulating function blocks together
with the data about their properties and, more importantly,
their functionality in a way that will enable diminishing of
the time to market and facilitate effective rapid object
oriented development of automation systems.

@@

%%     effective reuse of software
Object oriented system development as presented in the
IEC~61499 standard is ideal for the purpose that is is
designed for but not enough for achieving {\it effective
  software reuse} in automation systems development.

% grouping software objects in functional units (encapsulation)
% abstraction of functionality (views)
% properties of the functional unit (attributes)

@@

%%     easier integration and deployment of software
Leveraging effective software reuse and decentralized
software development \textit{makes integration and
  deployment much easier}. System integrator's task is
hereby reduced to picking the right software objects from
the library and connecting them in correct patterns for the
specific application.

@@

%%     all of these result in rapid development of automation systems
The arguments presented are enough to support the idea that
the software objects encapsulated with the information about
their usage will increase the speed of the development of
the automation systems.

After a formal definition of the encapsulation the benefits
beyond the ones discussed above will be presented followed
by the presentation about the implementation issues and the
support in Supremica that is planned for such data objects.

\section{Definition}
%% Definition. 
%%     multi view objects
An \textbf{automation object} is defined as \textit{a set of
  software objects} encapsulated with a declaration of
\textit{services}, \textit{attributes} and \textit{views} of
the set.

The \textbf{set} specifies the applications, subapplications
and function blocks, as defined in \cite{iec:614991:2000},
contained within the automation object. Only one set per
automation object is defined and it contains \textit{all} of
the software objects required for the functionality of the
automation object.
% less dependency problems at the cost of storage, more on
% this after the definition

An \textbf{attribute} is a user defined and specified data that
describes some significant property of the automation
object.

A \textbf{view} is an interface to the object. Every
interface has at least one implementation.

A \textbf{service}

%% How this definition supports the arguments above

%% Further benefits of the the automation objects that could
%% not be described prior to definition
%%     views facilitate several different implementations of
%%     the same functionality for different hardware and it
%%     is the hardware vendors that should supply these

@@

%% implementation of automation objects
%%     archive of XML files
%%     attribute and view declarations in MetaInformation.xml

%% libraries 
%%     non-hierarchical pool of automation objects
%%     libraries  may be Internet repositories
%%     searching and sorting by multiple attributes
%%     searching and sorting by multiple views

>>>>

%% Intro
With the function blocks the main technological problem of
distributed automation has been solved. A general framework
for development and deployment of distributed automation
systems has been developed. What is still needed is a way of
encapsulating function blocks together with the data about
their properties and, more importantly, their functionality
in a way that will enable diminishing the time to market
and facilitate effective rapid object oriented development
of automation systems.

@@

%%     effective reuse of software
Object oriented system development as presented in the
IEC~61499 standard is ideal for the purpose that it is
designed for but not enough for achieving \emph{effective
  software reuse} in automation systems development.

@@

%%     easier integration and deployment of software
Leveraging effective software reuse and decentralized
software development \textit{makes integration and
  deployment much easier}. System integrator's task is
hereby reduced to picking the right software objects from
the library and connecting them for the specific
application.

@@

%%     all of these result in rapid development of
%%     automation systems
The arguments presented are enough to support the idea that
the software objects encapsulated with the information about
their usage will increase the speed of the development of
the automation systems.

%After a specification and a formal definition of the
%encapsulation the benefits beyond the ones discussed above
%will be presented followed by the presentation about the
%implementation issues and the support in Supremica that is
%planned for such data objects.

\section{Specification}
To realize all of the above mentioned arguments a new kind
of software objects are needed, preliminary called
\emph{automation objects}. Even though this kind of objects
are still very much a research subject the following is the
specification of the objects so far.

%Automation Object:
%* consists of models, controllers, views and
%  configuration registry
Automation objects consists of models, views, controllers
and configuration registry implemented using IEC-61499
function blocks and their inteerfaces. Models are
interchangable simulation models with varaying level of
abstraction. One model might be used for the simulation on a
high level of abstraction, typicaly behavioural model, and
another for the simulation on a lower level. This is then
used to implement dynamic zooming during the simulation. One
of the models will implement the communication with the
controlled equpiment thus allowing effortless switching
between simulation and acutal control. This will enable
gradual verification and on-line tuning of the big
automation systems by allowing the simulation of the system
components that are being configured or tuned while running
the components that are already configured.

Controllers are function blocks that control the model. The
best examples of controllers are regulators as PI- or
PID-regulator. On the higher level of the automation system
these can be configurable implementations of different
automation algorithms. This allows interchange of different
controlling strategies for easy verification with simulation
and the equipment.

Views are the function blocks allowing user interaction with
the automation object. These implement all the alowable ways
of interaction with the automation object. At the lower
levels of the automation system they will typically provide
different event and data interfaces depending on the user's
needs while at the higher leve they will implement full
graphical user interfaces for the operators.

%* service is a set of views that support some relevant task
%  for the connected controller  
%* is extensible with user defined services
%* supports replacement of services defined within the
%  object by user defined services
%* supports extension of services
%* supports distribution of services and model among
%  different computing resources
%* has a single topology involving model and services
%* has an access protection mechanism

@@

%% implementation of automation objects
%%   archive of XML files
%%   models, views, controllers and registry are declared in
%%   some kind of MetaInformation.xml

%% libraries 
%%   non-hierarchical pool of automation objects
%%   libraries  may be Internet repositories
%%   searching and sorting by multiple attributes/keys
%%   searching and sorting by services
